---
title: "Linear-Model with Prediction"
author: "Edward Gomez"
date: "2025-10-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
require(tidyverse)
require(tigerstats)
require(knitr)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

## Model1:SIMS~ARM

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() +ggtitle("SIMS vs ARM")+ theme(plot.title = element_text(hjust=0.5,size=20))
```

## Numerical Results 

```{r}
cor(SIMS~ARM,data=data)
```

## Inferential Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

## Create target
```{r}
target <- data.frame(ARM=90, GRIP=90)
```

## Predict Target Point of Model 1 
```{r}
predict(model.1,target,interval=c("prediction"))
```

### Linear Fit Model1

```{r}
basicNN + geom_point () + ggtitle("SIMS-ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method = lm)
```

## Model2:SIMS~GRIP

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicNN + geom_point() +ggtitle("SIMS vs GRIP")+ theme(plot.title = element_text(hjust=0.5,size=20))
```

## Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```

## Inferential Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

## Predict Target Point of Model 2

```{r}
predict(model.2,target,interval=c("prediction"))
```

## Linear Fit Model2

```{r}
basicNN + geom_point () + ggtitle("SIMS-GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method = lm)
```

## Model3:SIMS~ARMS+GRIP

## Numerical Results

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation of Model3 is higher than the other two which shows it is a better model.

## Inferential Results

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

The formula for model3 is -5.433871 + (0.037311)ARM + (0.024470)GRIP